Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
update intro par 1 and last. rearrange ideas

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016]. Indeed, predator populations are often composed of an assemblage of individuals that specialize in different foraging strategies or resources [@estesIndividualVariationPrey2003, tinkerFoodLimitationLeads2008, kernaleguenDeterminantsIndividualForaging2015, @phillipsCausesConsequencesIndividual2017]. It is now well established that such individual specialization cannot be attributed exclusively to sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011]. Indeed, a growing body of evidence suggests that ecological interactions may act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016]. For instance, competition, cooperation, and predation, are all expected to shape the foraging preferences of interacting individuals []. Yet, we have very limited knowledge on how intrinsic factors and ecological interactions reciprocally affect foraging specialization, and the underlying consequences of such among-individual differences for natural populations. *phillips 2017*

*on connait peu sur l'interaction entre facteurs internes et externes, et encore moins les consequences de ces interactions (fitness, etc)*

@@

*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécialisation est toujours là!! (bolnick, araujo, woo)* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*

@@

# Dernier paragraphe intro (Thèsez-vous)
Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization. This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial. First, we hypothesize that individual hunting behaviour will change with hunting experience. If experience reduces the costs of switching tactics, then predators should become more flexible through time. Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time. Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator foraging behaviour. Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable. Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal. Specialist hunters should fare better when prey variability is lower, while flexible hunters will fare better when prey variability is higher.

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016]. Indeed, predator populations are often composed of an assemblage of individuals that specialize in different foraging strategies or resources [@estesIndividualVariationPrey2003, tinkerFoodLimitationLeads2008, kernaleguenDeterminantsIndividualForaging2015, @phillipsCausesConsequencesIndividual2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to instrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016]. Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the underlying ecological and fitness consequences of such among-individual differences [@phillipsCausesConsequencesIndividual2017].

@@

@@

# Dernier paragraphe intro (Thèsez-vous)
Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization. This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial. First, we hypothesize that individual predator behaviour will change with hunting experience. If experience reduces the costs of switching between hunting tactics, then predators should become more flexible through time. Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time. Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics. Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable. Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal. Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
